Compositional Certified Resource Bounds

### 2015-04-13 paper/main.tex
added acks
minor changes

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University}
{\{first.last\}@yale.edu}

@@

\category{D.2.4}{Software Engineering}
{Software/Program Verification}
\category{F.3.1}{Logics and Meanings of Programs}
{Specifying and Verifying and Reasoning about Programs}

\terms Verification, Reliability

\keywords Quantitative Verification, Resource Bound Analysis, Static
Program Analysis, Amortized Analysis, LP Solving, Program Logic

@@

% \acks

% This research is based on work supported in part by NSF grants 1319671
% and 1065451, and DARPA grants FA8750-10-2-0254 and FA8750-12-2-0293.
% Any opinions, findings, and conclusions contained in this document are
% those of the authors and do not reflect the views of these agencies.

>>>>

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University}
{\{quentin.carbonneaux, jan.hoffmann, zhong.shao\}@yale.edu}

@@

\category{D.2.4}{Software Engineering}
{Software/Program Verification}
\category{F.3.1}{Logics and Meanings of Programs}
{Specifying and Verifying and Reasoning about Programs}
\vspace{-3pt}
\terms Verification, Reliability
\vspace{-3pt}
\keywords Quantitative Verification, Resource Bound Analysis, Static
Analysis, Amortized Analysis, LP Solving, Program Logic

@@

\acks

This research is based on work supported in part by NSF grants 1319671
and 1065451, and DARPA grants FA8750-10-2-0254 and FA8750-12-2-0293.
Any opinions, findings, and conclusions contained in this document are
those of the authors and do not reflect the views of these agencies.
